Linear response theory for core set identification

### 2012-07-24 writedown/linear.response/langevin.tex
add non linear response theory

\subsection{Numerical tests}

\subsubsection{The tilting double-well potential}

@@

\subsubsection{Splitting single-well potential}

>>>>

\subsection{General response theory for core set identification}

Here, we assume that the system undergoes a series of perturbations,
which are denoted by $F^0_e(t),\ F^1_e(t),\ \cdots,\ F^i_e(t),\ \cdots$.
Here, $F^0_e(t) = 0$.
The measure for the trajectory space
$\mc\{\vect x, 0; t\}$
is given by
$\mathcal P_0^\beta[\vect X_s],\ \mathcal P_1^\beta[\vect X_s],\ \cdots,\
\mathcal P_i^\beta[\vect X_s], \cdots$, respectively.
The measure for the quenching trajectory are denoted by
$\mathcal P_{0,t}^{2\beta}[\vect X_\eta],\
\mathcal P_{1,t}^{2\beta}[\vect X_\eta],\ \cdots,\
\mathcal P_{i,t}^{2\beta}[\vect X_\eta], \cdots$, respectively.
The notation $t$ on the subscript means the trajectory is branched from
the main trajectory at time $t$.
Now the phase space distribution $f_i(\vect x, t)$ for the
$i$-th perturbation can be studied in terms
of path integral:
  f_i(\vect x, t) =
  \int\dd\vect u\,
  f_i(\vect u, 0)
  \int_{\mc\{\vect u,0; \vect x,t\}}
  \dd\mathcal P_i^\beta[\vect X_s]
Applied by operator $\mt_\tau$, we have
  \mt_\tau f_i(\vect x, t)
  \int\dd\vect u f_i(\vect u, t)
  \int_{\mc\{\vect u,0; \vect x,\tau\}}
  \dd\mathcal P_{i,t}^{2\beta}[\vect X_\eta]\\
  \int\dd\vect v\,
  f_i(\vect v, 0)
  \int\dd\vect u
  \int_{\mc\{\vect v,0; \vect u,t\}}
  \dd\mathcal P_i^\beta[\vect X_s]  
  \int_{\mc\{\vect u,0; \vect x,\tau\}}
  \dd\mathcal P_{i,t}^{2\beta}[\vect X_\eta]
For the core set identification,
  [\proj\circ\mt_\tau f](\vect y, t)
  \int\dd\vect v\,
  f_i(\vect v, 0)
  \int\dd\vect u
  \int_{\mc\{\vect v,0; \vect u,t\}}
  \dd\mathcal P_i^\beta[\vect X_s]  
  \int_{\mc\{\vect u,0; \tau\}}
  K_{\sigma,\vect y}(\vect X_\tau)\,
  \dd\mathcal P_{i,t}^{2\beta}[\vect X_\eta]  \\
  [\proj\circ\mt_0 f](\vect y, t)
  \int\dd\vect v\,
  f_i(\vect v, 0)
  \int_{\mc\{\vect v,0; t\}}
  K_{\sigma,\vect y}(\vect X_t)\,
  \dd\mathcal P_i^\beta[\vect X_s]  
  % \int_{\mc\{\vect u,0; \tau\}}
  % K_{\sigma,\vect y}(\vect X_\tau)\,
  % \dd\mathcal P_{i,t}^{2\beta}[\vect X_\eta]  
Here we assume that the system always starts from invariant measure,
i.e. $f_i(\vect x, 0) = f_{\inv}^\beta(\vect x)$, and that we have a
good sampling of the $(i-1)$-th perturbation, then
  [\proj\circ\mt_\tau f](\vect y, t)
  \int\dd\vect v\,
  f_\inv^\beta(\vect v)
  \int\dd\vect u
  \int_{\mc\{\vect v,0; \vect u,t\}}
  \dd\mathcal P_{i-1}^\beta[\vect X_s]  
  \int_{\mc\{\vect u,0; \tau\}}
  \dd\mathcal P_{i-1,t}^{2\beta}[\vect X_\eta]\cdot
  K_{\sigma,\vect y}(\vect X_\tau)\,
  \frac
  {\dd\mathcal P_{i}^\beta[\vect X_s]}
  {\dd\mathcal P_{i-1}^\beta[\vect X_s]}
  \frac
  {\dd\mathcal P_{i,t}^{2\beta}[\vect X_\eta]}
  {\dd\mathcal P_{i-1,t}^{2\beta}[\vect X_\eta]}
  [\proj\circ\mt_0 f](\vect y, t)
  \int\dd\vect v\,
  f_{\inv}^\beta(\vect v)
  \int_{\mc\{\vect v,0; t\}}
  \dd\mathcal P_{i-1}^\beta[\vect X_s]
  K_{\sigma,\vect y}(\vect X_t)\,
  \frac
  {\dd\mathcal P_{i}^\beta[\vect X_s]}
  {\dd\mathcal P_{i-1}^\beta[\vect X_s]}  
  % \int_{\mc\{\vect u,0; \tau\}}
  % K_{\sigma,\vect y}(\vect X_\tau)\,
  % \dd\mathcal P_{i,t}^{2\beta}[\vect X_\eta]  
Here
\begin{align}\label{eqn:exact-ratio-1}
  \frac
  {\dd\mathcal P_{i}^\beta[\vect X_s]}
  {\dd\mathcal P_{i-1}^\beta[\vect X_s]}  
  \Delta F_e^{i-1}(s)\,
  \frac{1}\sigma\int_0^t
  \vect D(\vect q_s,\vect p_s)\cdot\dd\vect W_s
  [\Delta F_e^{i-1}(s)]^2\,
  \frac 1{2\sigma}\int_0^t
  \vect D^2(\vect q_s,\vect p_s)\,\dd s
  \bigg\}\\\label{eqn:exact-ratio-2}
  \frac
  {\dd\mathcal P_{i,t}^{2\beta}[\vect X_\eta]}
  {\dd\mathcal P_{i-1,t}^{2\beta}[\vect X_\eta]}
  \Delta F_e^{i-1}(t)\,
  \frac{1}\sigma\int_0^\tau
  \vect D(\vect q_\eta,\vect p_\eta)\cdot\dd\vect W_\eta
  [\Delta F_e^{i-1}(t)]^2\,
  \frac 1{2\sigma}\int_0^\tau
  \vect D^2(\vect q_\eta,\vect p_\eta)\,\dd \eta
where $\Delta F_e^{i-1}(t) = F_e^{i}(t) - F_e^{i-1}(t) $.
If the trajectory at perturbation $ F_e^{i-1}(t) $ is well sampled, then
\eqref{eqn:exact-ratio-1} and \eqref{eqn:exact-ratio-2} can be measured
without linear approximation.

\section{Numerical tests}

\subsection{The tilting double-well potential}

@@

\subsection{Splitting single-well potential}
